%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}
\enlargethispage{-2\baselineskip}
\begin{document}
\header{robert}{gawdzik}
       {software developer}


% In the aside, each new line forces a line break
\begin{aside}
    \section{contact}
    \href{mailto:robert.gawdzik@uwaterloo.ca}{robert.gawdzik\\@uwaterloo.ca}
    ~
     (226) 606-4314
    \href{http://gawdzik.net}{gawdzik.net}
    \href{http://www.github.com/rgawdzik}{github.com/rgawdzik}
  \section{languages}
     C++
     C\#.NET
     Java
     PHP
     JavaScript/Web
     Haskell
     Lisp
     Objective-C
      \section{databases}
         MySQL
         NoSQL
         MSSQL
      \section{tools}
         IntelliJ
         Eclipse
         Visual Studio
      \section{web}
         REST
         Socket-IO
         node.js
         MEAN.io
      \section{3D}
         OpenGL
         Vector Mathematics
         XNA 2D  \& 3D
       \section{UNIX}
       Bash
       XMonad
       Vim
       sysadmin
\end{aside}

\section{introduction}
I am a Computer Science student studying at the University of Waterloo. I have a passion for software development, emerging technologies, and theoretical computer science.
\section{experience}

\begin{entrylist}
  \entry
    {\emph{06-08, 2013}}
    {Desire2Learn, {\normalfont \emph{Downtown Toronto}}}
    {Software Developer}
    {Developed software for the next generation of e-learning.
         \begin{itemize}
	\item Worked on improving the existing Learning Repository REST APIs.
	\item Improved Desire2Learn extensibility by developing integration points using the APIs.
	\item Used SVN tools, agile methodology, and code reviews to complete tasks effectively.
	\end{itemize}}
  \entry
    {\emph{01-06, 2013}}
    {Microsoft Canada, {\normalfont \emph{Toronto}}}
    {Microsoft Student Partner}
    {Microsoft student event coordinator and representative. Involved hosting and going to developer events all over Toronto promoting and developing for the Microsoft ecosystem.}
  \entry
    {\emph{2011-2013}}
    {Byte Code Canada, {\normalfont \emph{Toronto}}}
    {Indie Developer}
    {Published apps and games for different emerging platforms independently, sponsored by Intel, Nokia, and Microsoft.}
\end{entrylist}

\section{major personal projects}

\begin{entrylist}
\entry
    {\emph{2011-2012}}
    {Soar}
    {\href{https://github.com/rgawdzik/Soar}{www.github.com/rgawdzik/Soar}}
    {My interests in graphics and game engines pursued me to create Soar 2D and Soar 3D (open source).
    \begin{itemize}
      \item Both featured awesome massive space ship battles with many missions.
      \item Gathered 100,000 page views from reddit.
      \end{itemize}}
  \entry
    {\emph{2012}}
    {Sim Trader}
    {}
    {Due to my fascination for stock markets, I developed a virtual stock market in under a week for an app-a-thon.
    \begin{itemize}
    \item Social features such as a chat, leaderboards, and achievements. 
    \item One of the first Windows 8 apps, earning 30,000+ downloads.
    \end{itemize}}
\end{entrylist}


\section{education}

\begin{entrylist}
  \entry
    {\emph{2013-2018}}
    {Computer Science, Co-op, University of Waterloo}
    { }
    {\emph{Candidate for Bachelor of Computer Science, Software Engineering Option}}
  \entry
    {\emph{2009-2013}}
    {High School, Michael Power Saint Joseph}
    {}
    {}
\end{entrylist}

\section{awards}
	2013 Ontario Skills Canada Virtual Robotics Provincial 1st Place Winner \newline
	2012 Stack Overflow International App Contest – 1st Place (Work Category) \newline
	2012 Intel International AppUp Round 1 Winner \newline
	2012 Microsoft International App-a-thon Category Winner (Finance Category) \newline
	2013 MPSJ Top Computer Science Student
	

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
